Scrutinizing the linear variable importance of local explanations of non-linear models with animated linear projections

### 2022-01-02 _paper.rmd
typo

<!-- Local explanations -->
Explanabile Artificial Intelligence (XAI) is a recent branch of research that tries to increase the interpretability of black-box models. One way to do so is to use _local explanations_, which take a variable attribution approach to bring transparency to a model. Local explanations attempt to approximate linear variable importance at the location of one observation. Even with a linear space or local approximation, the number of terms is usually sizable, thus challenging to visualize comprehensively.

>>>>

<!-- Local explanations -->
Explainable Artificial Intelligence (XAI) is a recent branch of research that tries to increase the interpretability of black-box models. One way to do so is to use _local explanations_, which take a variable attribution approach to bring transparency to a model. Local explanations attempt to approximate linear variable importance at the location of one observation. Even with a linear space or local approximation, the number of terms is usually sizable, thus challenging to visualize comprehensively.
